Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/model.tex
broke ref sorted

\noindent
We define a lattice model of array access patterns which serves as
a semantic model of our specification language and model of array
access patterns in source code. This model (1) used to explain the
meaning of our specifications; (2) as a basis for the inference and
checking algorithms (\Cref{sec:analysis}); (3) justifies an equational
theory for specifications in the next section; (4) is used to optimise
specifications using lattice identities; and (5) can be used to guide
correct implementations.

>>>>

\noindent
We define a lattice model of array access patterns which serves as
a semantic model of our specification language and model of array
access patterns in source code. This model (1) used to explain the
meaning of our specifications; (2) as a basis for the inference and
checking algorithms (\Cref{sec:algorithms}); (3) justifies an equational
theory for specifications in the next section; (4) is used to optimise
specifications using lattice identities; and (5) can be used to guide
correct implementations.
